---
title: "BSS_20200508"
output: html_notebook
---

In order to use the R package $Knockoff$, we implemented a part of our simulations in R.

### Preparations
```{r message=FALSE}
library(mvtnorm)
library(knockoff)
```

### Function: Generating Gaussian Samples
```{r}
generate_normaldata<-function(n,p,rho,SNR,beta0){
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  mu1<-seq(length=p,from=0,to=0)
  X<-rmvnorm(n,mu1,sigma)
  X<-as.data.frame(X)
  for(i in c(1:p)){
    X[,i]<-X[,i]-mean(X[,i])
    tt<-sqrt(X[,i]%*%X[,i])
    X[,i]<-X[,i]/tt
  }
  X<-as.matrix(X)
  tt1<-t(beta0)%*%sigma%*%beta0
  sigma_square<-tt1/SNR
  I<-diag(1,nr=n,nc=n)
  new_sigma<-as.numeric(sigma_square)*I
  Y<-rmvnorm(1,X%*%beta0,new_sigma)
  return(list(X,Y))
}
```

### Function: Metrics--FDR,TPR
```{r}
FDR<-function(betahat,s){
  return(length(which(betahat>s))/length(betahat))
}
TPR<-function(betahat,s){
  return(length(which(1:s %in% betahat))/s)
} 
```

### Test: Metrics
```{r}

```

### Set $FDR$ control's
```{r}
FDR_control<-seq(0.34,0.7,0.04)
```

### Actual Tests
#### Test 1: Low Setting, High-Noise, $\rho$ = 0.35
```{r warning=FALSE}
# Store FDR and TPR
TPR_1<-rep(0,10)
FDR_1<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**0.05)
for(i in 1:10){
  TPR_1_temp<-rep(0,100)
  FDR_1_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_1_temp[j]<-TPR(beta_knock,s)
       FDR_1_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_1[i]<-mean(TPR_1_temp)
  FDR_1[i]<-mean(FDR_1_temp)
}
print('FDR_1:')
print(FDR_1)
print('TPR_1')
print(TPR_1)
```

#### Test 2: Low Setting, High-Noise, $\rho$ = 0.70
```{r warning=FALSE}
# Store FDR and TPR
TPR_2<-rep(0,10)
FDR_2<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**0.05)
for(i in 1:10){
  TPR_2_temp<-rep(0,100)
  FDR_2_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_2_temp[j]<-TPR(beta_knock,s)
       FDR_2_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_2[i]<-mean(TPR_2_temp)
  FDR_2[i]<-mean(FDR_2_temp)
}
print('FDR_2:')
print(FDR_2)
print('TPR_2:')
print(TPR_2)
```

#### Test 3: Low Setting, Medium-Noise, $\rho$ = 0.35
```{r warning=FALSE}
# Store FDR and TPR
TPR_3<-rep(0,10)
FDR_3<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10)
for(i in 1:10){
  TPR_3_temp<-rep(0,100)
  FDR_3_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_3_temp[j]<-TPR(beta_knock,s)
       FDR_3_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_3[i]<-mean(TPR_3_temp)
  FDR_3[i]<-mean(FDR_3_temp)
}
print('FDR_3:')
print(FDR_3)
print('TPR_3:')
print(TPR_3)
```

#### Test 4: Low Setting, Medium-Noise, $\rho$ = 0.70
```{r warning=FALSE}
# Store FDR and TPR
TPR_4<-rep(0,10)
FDR_4<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
Lmatrix=chol(Sigma)
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10)
for(i in 1:10){
  TPR_4_temp<-rep(0,100)
  FDR_4_temp<-rep(0,100)
  for (j in 1:20) {
    X = matrix(rnorm(n*p),n) %*% Lmatrix
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_4_temp[j]<-TPR(beta_knock,s)
       FDR_4_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_4[i]<-mean(TPR_4_temp)
  FDR_4[i]<-mean(FDR_4_temp)
}
print('FDR_4:')
print(FDR_4)
print('TPR_4:')
print(TPR_4)
```

#### Test 5: Low Setting, Low-Noise, $\rho$ = 0.35
```{r warning=FALSE}
# Store FDR and TPR
TPR_5<-rep(0,10)
FDR_5<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
Lmatrix=chol(Sigma)
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**6)
for(i in 1:10){
  TPR_5_temp<-rep(0,100)
  FDR_5_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% Lmatrix
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_5_temp[j]<-TPR(beta_knock,s)
       FDR_5_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_5[i]<-mean(TPR_5_temp)
  FDR_5[i]<-mean(FDR_5_temp)
}
print('FDR_5:')
print(FDR_5)
print('TPR_5:')
print(TPR_5)
```

#### Test 6: Low Setting, Low-Noise, $\rho$ = 0.70
```{r warning=FALSE}
# Store FDR and TPR
TPR_6<-rep(0,10)
FDR_6<-rep(0,10)
# Set generate parameters 1
n=100
p=50
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
Lmatrix=chol(Sigma)
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=45,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**6)
for(i in 1:10){
  TPR_6_temp<-rep(0,100)
  FDR_6_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% Lmatrix
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_6_temp[j]<-TPR(beta_knock,s)
       FDR_6_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_6[i]<-mean(TPR_6_temp)
  FDR_6[i]<-mean(FDR_6_temp)
}
print('FDR_6:')
print(FDR_6)
print('TPR_6:')
print(TPR_6)
```

```{r warning=FALSE}
#### Test 7: Medium Setting, High-Noise, $\rho$ = 0.35
# Store FDR and TPR
TPR_7<-rep(0,10)
FDR_7<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**0.05)
for(i in 1:10){
  TPR_7_temp<-rep(0,100)
  FDR_7_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_7_temp[j]<-TPR(beta_knock,s)
       FDR_7_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_7[i]<-mean(TPR_7_temp)
  FDR_7[i]<-mean(FDR_7_temp)
}
print('FDR_7:')
print(FDR_7)
print('TPR_7:')
print(TPR_7)

```

```{r warning=FALSE}
#### Test 8: Medium Setting, High-Noise, $\rho$ = 0.70
# Store FDR and TPR
TPR_8<-rep(0,10)
FDR_8<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**0.05)
for(i in 1:10){
  TPR_8_temp<-rep(0,100)
  FDR_8_temp<-rep(0,100)
  for (j in 1:100) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_8_temp[j]<-TPR(beta_knock,s)
       FDR_8_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_8[i]<-mean(TPR_8_temp)
  FDR_8[i]<-mean(FDR_8_temp)
}
print('FDR_8:')
print(FDR_8)
print('TPR_8:')
print(TPR_8)

```


```{r warning=FALSE}
#### Test 9: Medium Setting, Medium-Noise, $\rho$ = 0.35
# Store FDR and TPR
TPR_9<-rep(0,10)
FDR_9<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10)
for(i in 1:10){
  TPR_9_temp<-rep(0,100)
  FDR_9_temp<-rep(0,100)
  for (j in 1:20) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_9_temp[j]<-TPR(beta_knock,s)
       FDR_9_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_9[i]<-mean(TPR_9_temp)
  FDR_9[i]<-mean(FDR_9_temp)
}
print('FDR_9:')
print(FDR_9)
print('TPR_9:')
print(TPR_9)
```

```{r warning=FALSE}
#### Test 10: Medium Setting, Medium-Noise, $\rho$ = 0.70
# Store FDR and TPR
TPR_10<-rep(0,10)
FDR_10<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10)
for(i in 1:10){
  TPR_10_temp<-rep(0,100)
  FDR_10_temp<-rep(0,100)
  for (j in 1:20) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_10_temp[j]<-TPR(beta_knock,s)
       FDR_10_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_10[i]<-mean(TPR_10_temp)
  FDR_10[i]<-mean(FDR_10_temp)
}
print('FDR_10:')
print(FDR_10)
print('TPR_10:')
print(TPR_10)
```

```{r warning=FALSE}
#### Test 11: Medium Setting, Low-Noise, $\rho$ = 0.35
# Store FDR and TPR
TPR_11<-rep(0,10)
FDR_11<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.35
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**6)
for(i in 1:10){
  TPR_11_temp<-rep(0,100)
  FDR_11_temp<-rep(0,100)
  for (j in 1:20) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_11_temp[j]<-TPR(beta_knock,s)
       FDR_11_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_11[i]<-mean(TPR_11_temp)
  FDR_11[i]<-mean(FDR_11_temp)
}
print('FDR_11:')
print(FDR_11)
print('TPR_11:')
print(TPR_11)
```

```{r warning=FALSE}
#### Test 12: Medium Setting, Low-Noise, $\rho$ = 0.70
# Store FDR and TPR
TPR_12<-rep(0,10)
FDR_12<-rep(0,10)
# Set generate parameters 1
n=500
p=100
s=5
# Set generate parameters 2
mu=rep(0,p)
rho=0.7
Sigma=toeplitz(rho^(0:(p-1)))
beta0<-as.matrix(c(seq(length=5,from=1,to=1),seq(length=95,from=0,to=0)))
sigma=sqrt(t(beta0)%*%Sigma%*%beta0/10**6)
for(i in 1:10){
  TPR_12_temp<-rep(0,100)
  FDR_12_temp<-rep(0,100)
  for (j in 1:20) {
    X = matrix(rnorm(n*p),n) %*% chol(Sigma)
    Y = X%*%beta0+rnorm(n,0,sigma)
    beta_knock<-as.vector(unlist(knockoff.filter(X,Y,fdr=FDR_control[i])[7]))
    if(length(beta_knock>0)){
       TPR_12_temp[j]<-TPR(beta_knock,s)
       FDR_12_temp[j]<-FDR(beta_knock,s)
    }
  }
  print(i)
  TPR_12[i]<-mean(TPR_12_temp)
  FDR_12[i]<-mean(FDR_12_temp)
}
print('FDR_12:')
print(FDR_12)
print('TPR_12:')
print(TPR_12)

```