---
title: "L0_20200417"
author: "Shihao Wu"
date: "2020/4/14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mvtnorm)
library(ggplot2)
library(glmnet)
library(lars)
library(devtools)
library(gurobi)
set.seed(0)
```

For each of the four dataset size types, I conducted performance comparison between the 3 algorithms with changing SNR value.

### Functions 
```{r}
solve_lasso_descent<-function(Y,X,lambda){
  nnn<-dim(X)[1]
  ppp<-dim(X)[2]
  beta_old<-seq(length=ppp,from=0,to=0)
  beta_new<-seq(length=ppp,from=0.1,to=0.1)
  while ( t(beta_new-beta_old)%*%(beta_new-beta_old)>0.0001 ) {
    beta_old<-beta_new
    for(j in c(1:ppp)){
      rho<-0
      for(i in c(1:nnn)){
        rho<-rho+X[i,j]*(Y[i]-t(X[i,])%*%beta_old+X[i,j]*beta_old[j])
      }
      zzz<-t(X[,j])%*%X[,j]
      if(-rho>lambda/2){beta_new[j]<-(rho+lambda/2)/zzz}
      else if((rho>=(-lambda/2))|(rho<=lambda/2)){beta_new[j]<-0}
      else if(rho>lambda/2){beta_new[j]<-(rho-lambda/2)/zzz}
    }
  }
  return(beta_new)
}

solve_Lasso<-function(Y,X,beta0,rho,SNR){
# test dataset
  p<-dim(X)[2]
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  test_mu<-seq(length=p,from=0,to=0)
  X_test<-rmvnorm(100,test_mu,sigma)
  X_test<-as.data.frame(X_test)
  for(i in c(1:p)){
    X_test[,i]<-X_test[,i]-mean(X_test[,i])
    tt<-sqrt(X_test[,i]%*%X_test[,i])
    X_test[,i]<-X_test[,i]/tt
  }
  X_test<-as.matrix(X_test)
  tt1<-t(beta0)%*%sigma%*%beta0
  sigma_square<-as.numeric(tt1/SNR)
  I<-diag(1,nr=100,nc=100)
  Y_test<-t(rmvnorm(1,X_test%*%beta0,sigma_square*I))
# tuning
  lambda_max<-norm(t(X)%*%Y,type='I')
  p<-dim(X)[2]
  lambda<-seq(length=10,from=0.1*lambda_max,to=0.9*lambda_max)
  score<-c()
  beta_result<-c()
  j=1
  for (lambda1 in lambda) {
    beta<-solve_lasso_descent(Y,X,lambda1)
    score[j]<- t(Y_test-X_test%*%beta)%*%(Y_test-X_test%*%beta)
    if (score[j]==min(score)){
      beta_result<-beta
    }
    j=j+1
  }
  for (i in c(1:10)) {
    if (score[i]==min(score)){
       break
    }
  }
  return(list(beta_result,lambda[i]))
}

solve_ridge_regression<-function(Y,X,lambda){
  p<-dim(X)[2]
  I<-diag(1,nr=p,nc=p)
  return(solve(t(X)%*%X+lambda*I)%*%t(X)%*%Y)
}

solve_relaxed_Lasso<-function(Y,X,beta0,rho=0.35,SNR){
  # test dataset
  p<-dim(X)[2]
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  test_mu<-seq(length=p,from=0,to=0)
  X_test<-rmvnorm(100,test_mu,sigma)
  X_test<-as.data.frame(X_test)
  for(i in c(1:p)){
    X_test[,i]<-X_test[,i]-mean(X_test[,i])
    tt<-sqrt(X_test[,i]%*%X_test[,i])
    X_test[,i]<-X_test[,i]/tt
  }
  X_test<-as.matrix(X_test)
  tt1<-t(beta0)%*%sigma%*%beta0
  sigma_square<-as.numeric(tt1/SNR)
  I<-diag(1,nr=100,nc=100)
  Y_test<-t(rmvnorm(1,X_test%*%beta0,sigma_square*I))
# active set
  beta_lasso<-as.matrix(as.data.frame(solve_Lasso(Y,X,beta0,0.35,SNR)[1]))
  lambda<-as.numeric(solve_Lasso(Y,X,beta0,0.35,SNR)[2])
  active_set<-c()
  i=1
  for (j in c(1:p)) {
    if(beta_lasso[j]!=0){
      active_set[i]<-j
      i=i+1
    }
  }
  score<-c()
  gamma<-seq(length=10,from=0,to=1)
  beta_champion<-matrix(nr=p,nc=1)
# tuning
  for (kk in c(1:10)) {
    beta_active<-solve(t(X[,active_set])%*%X[,active_set])%*%(t(X[,active_set])%*%Y-gamma[kk]*lambda*as.matrix(sign(beta_lasso[active_set])))
    beta_relax<-c()
    count<-1
    for (i in c(1:p)) {
      if(i %in% active_set){
        beta_relax[i]<-beta_active[count]
        count<-count+1
      }
      else{beta_relax[i]<-0}
    }
    score[kk]<-t(Y_test-X_test%*%beta_relax)%*%(Y_test-X_test%*%beta_relax)
    if(score[kk]==max(score)){beta_champion<-beta_relax}
  }
#  beta_ridge<-solve_ridge_regression(Y,X,lambda)
#  gamma<-seq(length=10,from=0,to=1)
#  score<-c()
#  beta_champion<-matrix(nr=p,nc=1)
#  for (i in c(1:10)){
#    beta_relax<-gamma*beta_lasso+(1-gamma)*beta_ridge
#    score[i]<-t(Y_test-X_test%*%beta)%*%(Y_test-X_test%*%beta)
#    if(score[i]==max(score)){beta_champion<-beta_relax}
#  }
  return(beta_champion)
}

solve_discrete_firstorder<-function(Y,X,epsilon,k){
  L<-max(eigen(t(X)%*%X)$values)
  p<-dim(X)[2]
  aa<-seq(length=k,from=1,to=1)
  bb<-seq(length=p-k,from=0,to=0)
  beta_new<-seq(length=p,from=0,to=0)
  beta_old<-c(aa,bb)
  while ( t(beta_new-beta_old)%*%(beta_new-beta_old)>epsilon ) {
    beta_old<-beta_new
    tt<-beta_old-(1/L)*(t(X)%*%X%*%beta_old-t(X)%*%Y)
    beta_new<-seq(length=p,from=0,to=0)
    tt_sort<-sort(unique(abs(tt)),decreasing=TRUE)
    for(i in c(1:k)){
      for(j in c(1:p)){
        if(beta_old[j]==tt_sort[i]){
          beta_new[j]<-beta_old[j]
          break
        }
      }
    }
  }
  index<-c()
  k=1
  for(i in c(1:p)){
    if(beta_new[i]!=0){
      index[k]<-i
      k=k+1
    }
  }
  return(solve(t(X[,index])%*%x[,index])%*%t(X[,index])%*%Y)
}

solve_Subset<-function(Y,X,k,epsilon,Ptype=T,UB){
  warm_start<-solve_discrete_firstorder(Y,X,epsilon,k)
  pp<-dim(X)[2]
  nn<-dim(X)[1]
  zeros_p<-diag(0,nr=pp,nc=pp)
  zeros_np<-matrix(0,nr=nn,nc=pp)
  ones_p<-diag(1,nr=pp,nc=pp)
  ones_n<-diag(1,nr=nn,nc=nn)
# Estimate M_U  
  M_U_hlist<-c()
  M_U_llist<-c()
  for (i in c(1:p)){
    model<-list()
    model$obj<-c(rep(0,i-1),1,rep(0,pp-i),rep(0,nn))
    qc<-list()
    qc$Qc<-ones_n
    qc$rhs<-2*UB
    model$quadcon<-list(qc)
  }
# Estimate M_tau
  M_tau<-c()
  for (i in c(1:p)) {
    
  }
# Least Square
  if(Ptype){### MIO formation (9)
    model<-list()
    model$Q<-cbind(rbind(1/2*t(X)%*%X,zero_p),rbind(zeros_p,zeros_p))
    model$obj<--t(X)%*%Y
    model$A<-rbind(c(rep(0,pp),rep(1,pp)),cbind(ones_p,zeros_p),cbind(ones_p,zeros_p))
    model$sense<-c(rep('<=',pp+1),rep('>=',pp))
    model$rhs<-c(p-k,rep(-M_U,p),rep(M_U,p))
    model$vtype<-c(rep('C',pp),rep('B',pp))
    sos<-list()
    for (i in c(1:pp)){
      sos_int<-list()
      sos_int$type<-1
      sos_int$index<-c(i,i+pp)
      sos_int$weight<-c(1,1)
      sos[[i]]<-sos_int
    }
    model$sos<-sos
    return(gurobi(model)$x[c(1:p)])
  }
# High Dimensional
  else{### MIO formation (10)
    
  }
}

generate_normaldata<-function(n,p,rho,SNR,beta0){
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  mu1<-seq(length=p,from=0,to=0)
  X<-rmvnorm(n,mu1,sigma)
  X<-as.data.frame(X)
  for(i in c(1:p)){
    X[,i]<-X[,i]-mean(X[,i])
    tt<-sqrt(X[,i]%*%X[,i])
    X[,i]<-X[,i]/tt
  }
  X<-as.matrix(X)
  tt1<-t(beta0)%*%sigma%*%beta0
  sigma_square<-tt1/SNR
  I<-diag(1,nr=n,nc=n)
  new_sigma<-as.numeric(sigma_square)*I
  Y<-rmvnorm(1,X%*%beta0,new_sigma)
  return(list(X,Y))
}

metric_1<-function(rho,p,beta0,betahat){ 
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  tt1<-t(beta0-betahat)%*%sigma%*%(beta0-betahat)
  tt2<-t(beta0)%*%sigma%*%beta0
  return(as.numeric(tt1/tt2))
}

metric_2<-function(betahat,beta0,rho,p,SNR){
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  tt1<-t(beta0-betahat)%*%sigma%*%(beta0-betahat)
  tt2<-t(beta0)%*%sigma%*%beta0
  sigma_square<-tt2/SNR
  return((tt1+sigma_square)/sigma_square)
}

metric_3<-function(betahat,beta0,rho,p,SNR){
  sigma<-matrix(nr=p,nc=p)
  for(i in c(1:p)){
    for(j in c(1:p)){
      sigma[i,j]<-rho^(abs(i-j))
    }
  }
  tt1<-t(beta0-betahat)%*%sigma%*%(beta0-betahat)
  tt2<-t(beta0)%*%sigma%*%beta0
  sigma_square<-tt2/SNR
  return(1-(tt1+sigma_square)/(tt2+sigma_square))
}

metric_4<-function(betahat){
  return(sum(betahat!=0))
}

metric_5<-function(X,beta0,betahat){
  n<-dim(X)[1]
  count=0
  for(i in c(1:n)){
    tt1<-t(X[i,])%*%beta0-t(X[i,])%*%betahat
    tt2<-t(X[i,])%*%beta0
    if(tt1^2/tt2^2>0.05){count=count+1}
  }
  return(count/n)
}

```


### Dataset Size: low

Generate Datasets with different SNR:
```{r warning=FALSE}
SNR<-c(0.05,0.09,0.14,0.25,0.42,0.71,1.22,2.07,3.52,6.00)
SNR<-10^(SNR)
beta01<-seq(length=5,from=1,to=1)
beta02<-seq(length=5,from=0,to=0)
beta0<-as.matrix(c(beta01,beta02))
X11<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[1],beta0)[1]))
Y11<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[1],beta0)[2])))
X12<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[2],beta0)[1]))
Y12<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[2],beta0)[2])))
X13<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[3],beta0)[1]))
Y13<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[3],beta0)[2])))
X14<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[4],beta0)[1]))
Y14<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[4],beta0)[2])))
X15<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[5],beta0)[1]))
Y15<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[5],beta0)[2])))
X16<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[6],beta0)[1]))
Y16<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[6],beta0)[2])))
X17<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[7],beta0)[1]))
Y17<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[7],beta0)[2])))
X18<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[8],beta0)[1]))
Y18<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[8],beta0)[2])))
X19<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[9],beta0)[1]))
Y19<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[9],beta0)[2])))
X10<-as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[10],beta0)[1]))
Y10<-t(as.matrix(as.data.frame(generate_normaldata(100,10,0.35,SNR[10],beta0)[2])))
X1<-list(X11,X12,X13,X14,X15,X16,X17,X18,X19,X10)
Y1<-list(Y11,Y12,Y13,Y14,Y15,Y16,Y17,Y18,Y19,Y10)
```
Estimators of Three types and calculate the metrics:
```{r}
beta_Lasso_1<-matrix(nr=10,nc=10)
beta_bestsubset_1<-matrix(nr=10,nc=10)
beta_relaxed_Lasso_1<-matrix(nr=10,nc=10)
for (i in c(1:10)) {
  beta_Lasso_1[,i]<-solve_Lasso()
  beta_bestsubset_1[,i]<-solve_Subset()
  beta_relaxed_Lasso_1[,i]<-solve_relaxed_Lasso()
}
```
Graphs:
```{r}


```


### Dataset Size: medium
Generate Datasets with different SNR:
```{r}
SNR<-c(0.05,0.09,0.14,0.25,0.42,0.71,1.22,2.07,3.52,6.00)
SNR<-10^(SNR)
beta01<-seq(length=5,from=1,to=1)
beta02<-seq(length=95,from=0,to=0)
beta0<-c(beta01,beta02)
X21<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[1],beta0)[1]))
Y21<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[1],beta0)[2])))
X22<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[2],beta0)[1]))
Y22<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[2],beta0)[2])))
X23<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[3],beta0)[1]))
Y23<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[3],beta0)[2])))
X24<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[4],beta0)[1]))
Y24<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[4],beta0)[2])))
X25<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[5],beta0)[1]))
Y25<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[5],beta0)[2])))
X26<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[6],beta0)[1]))
Y26<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[6],beta0)[2])))
X27<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[7],beta0)[1]))
Y27<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[7],beta0)[2])))
X28<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[8],beta0)[1]))
Y28<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[8],beta0)[2])))
X29<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[9],beta0)[1]))
Y29<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[9],beta0)[2])))
X20<-as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[10],beta0)[1]))
Y20<-t(as.matrix(as.data.frame(generate_normaldata(500,100,0.35,SNR[10],beta0)[2])))
X2<-list(X21,X22,X23,X24,X25,X26,X27,X28,X29,X20)
Y2<-list(Y21,Y22,Y23,Y24,Y25,X26,Y27,Y28,Y29,Y20)
```
Estimators of Three types and calculate the metrics:
```{r}
beta_Lasso_1<-matrix(nr=100,nc=10)
beta_bestsubset_1<-matrix(nr=100,nc=10)
beta_relaxed_Lasso_1<-matrix(nr=100,nc=10)
```
Graphs:
```{r}


```

### Dataset Size: high-5
Generate Datasets with different SNR:
```{r warning=FALSE}
SNR<-c(0.05,0.09,0.14,0.25,0.42,0.71,1.22,2.07,3.52,6.00)
SNR<-10^(SNR)
beta01<-seq(length=5,from=1,to=1)
beta02<-seq(length=995,from=0,to=0)
beta0<-c(beta01,beta02)
aaa<-generate_normaldata(50,1000,0.35,SNR[1],beta0)
X31<-as.matrix(as.data.frame(aaa[1]))
Y31<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[2],beta0)
X32<-as.matrix(as.data.frame(aaa[1]))
Y32<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[3],beta0)
X33<-as.matrix(as.data.frame(aaa[1]))
Y33<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[4],beta0)
X34<-as.matrix(as.data.frame(aaa[1]))
Y34<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[5],beta0)
X35<-as.matrix(as.data.frame(aaa[1]))
Y35<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[6],beta0)
X36<-as.matrix(as.data.frame(aaa[1]))
Y36<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[7],beta0)
X37<-as.matrix(as.data.frame(aaa[1]))
Y37<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[8],beta0)
X38<-as.matrix(as.data.frame(aaa[1]))
Y38<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[9],beta0)
X39<-as.matrix(as.data.frame(aaa[1]))
Y39<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(50,1000,0.35,SNR[10],beta0)
X30<-as.matrix(as.data.frame(aaa[1]))
Y30<-t(as.matrix(as.data.frame(aaa[2])))
X3<-list(X31,X32,X33,X34,X35,X36,X37,X38,X39,X30)
Y3<-list(Y31,Y32,Y33,Y34,Y35,Y36,Y37,Y38,Y39,Y30)
```
Estimators of Three types and calculate the metrics:
```{r}
beta_Lasso_1<-matrix(nr=1000,nc=10)
beta_bestsubset_1<-matrix(nr=1000,nc=10)
beta_relaxed_Lasso_1<-matrix(nr=1000,nc=10)
```
Graphs:
```{r}


```

### Dataset Size: high-10
Generate Datasets with different SNR:
```{r warning=FALSE}
SNR<-c(0.05,0.09,0.14,0.25,0.42,0.71,1.22,2.07,3.52,6.00)
SNR<-10^(SNR)
beta01<-seq(length=10,from=1,to=1)
beta02<-seq(length=990,from=0,to=0)
beta0<-c(beta01,beta02)
aaa<-generate_normaldata(100,1000,0.35,SNR[1],beta0)
X41<-as.matrix(as.data.frame(aaa[1]))
Y41<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[2],beta0)
X42<-as.matrix(as.data.frame(aaa[1]))
Y42<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[3],beta0)
X43<-as.matrix(as.data.frame(aaa[1]))
Y43<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[4],beta0)
X44<-as.matrix(as.data.frame(aaa[1]))
Y44<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[5],beta0)
X45<-as.matrix(as.data.frame(aaa[1]))
Y45<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[6],beta0)
X46<-as.matrix(as.data.frame(aaa[1]))
Y46<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[7],beta0)
X47<-as.matrix(as.data.frame(aaa[1]))
Y47<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[8],beta0)
X48<-as.matrix(as.data.frame(aaa[1]))
Y48<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[9],beta0)
X49<-as.matrix(as.data.frame(aaa[1]))
Y49<-t(as.matrix(as.data.frame(aaa[2])))
aaa<-generate_normaldata(100,1000,0.35,SNR[10],beta0)
X40<-as.matrix(as.data.frame(aaa[1]))
Y40<-t(as.matrix(as.data.frame(aaa[2])))
X4<-list(X41,X42,X43,X44,X45,X46,X47,X48,X44,X30)
Y4<-list(Y31,Y32,Y33,Y34,Y35,Y36,Y37,Y38,Y39,Y30)
```
Estimators of Three types and calculate the metrics:
```{r}
beta_Lasso_1<-matrix(nr=1000,nc=10)
beta_bestsubset_1<-matrix(nr=1000,nc=10)
beta_relaxed_Lasso_1<-matrix(nr=1000,nc=10)
```

Graphs:
```{r}


```

Clear up:
```{r}
rm(list=ls())
```
